Grove: A Convergent Collaborative Structure-Editor Calculus

### 2020-12-08 grove-paper.tex
Add links to some preliminary related work

Hazel
\citep{Omar:2019:10.1145/3290327}

@@

Pijul and Anu

@@

Git

Darcs

Unision?

Homotopical Patch Theorey: https://www.cambridge.org/core/journals/journal-of-functional-programming/article/homotopical-patch-theory/42AD8BB8A91688BCAC16FD4D6A2C3FE7

>>>>

\subsection{Trees}

\subsubsection{Structure editors}

Hazel~\citep{Omar:2019:10.1145/3290327}

\subsubsection{Tree diff}

J. W. Hunt and M. D. McIlroy. 1976. An Algorithm for Differential File Comparison. Technical Report CSTR 41. Bell Laboratories, Murray Hill, NJ.

Type-directed diffing of structured data \url{https://dl.acm.org/doi/10.1145/3122975.3122976}

  Approximating Tree Edit Distance through String Edit Distance \url{https://dl.acm.org/doi/10.5555/3118232.3118518}

  Meaningful change detection in structured data \url{https://dl.acm.org/doi/10.1145/253260.253266}

  An optimal decomposition algorithm for tree edit distance \url{https://dl.acm.org/doi/10.5555/2394539.2394560}

  Diff/TS: A Tool for Fine-Grained Structural Change Analysis \url{https://dl.acm.org/doi/10.1109/WCRE.2008.44}

An efficient algorithm for type-safe structural diffing \url{https://dl.acm.org/doi/10.1145/3341717}

  Precise Version Control of Trees with Line-Based Version Control Systems \url{https://dl.acm.org/doi/10.1007/978-3-662-54494-5_9}

  A survey on tree edit distance and related problems \url{https://dl.acm.org/doi/10.1016/j.tcs.2004.12.030}

  Cycle-aware minimization of acyclic deterministic finite-state automata \url{https://dl.acm.org/doi/10.1016/j.dam.2013.08.003}

  Computing the Edit-Distance between Unrooted Ordered Trees \url{https://dl.acm.org/doi/10.5555/647908.740125}

  Type-safe diff for families of datatypes \url{https://dl.acm.org/doi/10.1145/1596614.1596624}

  A Categorical Theory of Patches \url{https://dl.acm.org/doi/10.1016/j.entcs.2013.09.018}

  Type-directed diffing of structured data \url{https://dl.acm.org/doi/10.1145/3122975.3122976}

  The Semantics of Version Control \url{https://dl.acm.org/doi/10.1145/2661136.2661137}

  The Tree-to-Tree Correction Problem \url{https://dl.acm.org/doi/10.1145/322139.322143}

  Generic Diff3 for algebraic datatypes \url{https://dl.acm.org/doi/10.1145/2976022.2976026}

\subsection{Version Control}

Git \url{https://git-scm.com/}

Darcs \url{https://darcs.net/}

  Darcs: distributed version management in haskell \url{https://dl.acm.org/doi/10.1145/1088348.1088349}

Hg? \url{https://www.mercurial-scm.org/}

SVN \url{https://subversion.apache.org/}

Pijul and (Anu is a rewrite of Pijul and seems to have been subsumed into Pijul)

  \url{https://pijul.org/}
  \url{https://pijul.org/manual/theory.html}

  \url{https://tahoe-lafs.org/~zooko/badmerge/simple.html}

\subsection{Collaborative Editing}

@@

@@

\subsection{Synchronization}

Unision
\url{https://www.cis.upenn.edu/~bcpierce/unison/}
\url{https://www.cis.upenn.edu/%7Ebcpierce/papers/index.shtml#File%20Synchronization}

\subsection{TODO}

Homotopical Patch Theorey: \url{https://www.cambridge.org/core/journals/journal-of-functional-programming/article/homotopical-patch-theory/42AD8BB8A91688BCAC16FD4D6A2C3FE7}
Homotopical patch theory: \url{https://dl.acm.org/doi/10.1145/2628136.2628158}
